Generate data for NOBA cod ensemble modeling

### 2020-03-27 NOBAcod.Rmd
load annagecatch
test push
census configs for cod, start anncatch

NOBAom_cod_comp <- om_comps(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

@@

wageplot <- ggplot(wtage, aes(time, wtage)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

@@

>>>>

NOBAom_cod_comp <- om_comps(usersurvey = here("config/codsurvey.R"), 
                           userfishery = here("config/codfishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

@@

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

@@

```{r loadannagecatch}
# taken from existing load_nc

file.nc <- file.path(d.name, "outputnordic_runresults_01ANNAGECATCH.nc")

RNetCDF::close.nc(at_out)
```

ANNAGECATCH.nc variable names (first hundred): `r var_names_ncdf[1:100]`

ANNAGECATCH.nc variable names (last hundred): `r tail(var_names_ncdf, 100)`

ANNAGECATCH.nc timesteps: `r n_timesteps`

ANNAGECATCH.nc boxes: `r n_boxes`

ANNAGECATCH.nc layers: `r n_layers`

Catch file contains "IsFished" species discard at age and catch at age by fishery.
